Fictitious Play in Network Aggregative Games

### 2021-03-25 Documents/FP in NAGs/FPNAG.tex
Update FP in NAG

	Writing the NE condition out as a vector gives

@@

	in which $w_{-i}$ is a column vector containing $w_{ij}$ in the $j$'th element for all $j \in N(i)$ and 0 everywhere else (including in the $i$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product. So our condition becomes

	\begin{equation}
		\begin{bmatrix}
			x_1^* \\ . \\ . \\ . \\ x_N^*
		\end{bmatrix} \in
		\begin{bmatrix}
			\arg\max_{y \in \Delta_1} \bar{u}_1(y, (w_{-1}^T \otimes I_n) \begin{bmatrix}
				x_1^* \\ . \\ . \\ . \\ x_N^*
			\end{bmatrix}) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n) \begin{bmatrix}
			x_1^* \\ . \\ . \\ . \\ x_N^*
		\end{bmatrix}))
		\end{bmatrix}	.
	\end{equation}

@@

	Now, since the modified payoff $\bar{u}$ shares the same bilinear property as $u$, we can assert that it is continuous is its second argument. Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous (\ah{I think this argument is sound so I'm not sure if it's worth making it rigorous}). Furthermore, the map takes a point in $\Delta = \times_i \Delta_i$ into itself. As such, the space is non-empty, compact and convex.

	We can then apply Kakutani's Fixed Point Theorem

	\begin{theorem}[Kakutani]
		If S is a nonempty, compact, convex set in $\mathbb{R}^n$ and $\Phi : S \rightarrow \textbf{P}(S)$ ($\textbf{P}(S)$ is the power set of S) is upper semi-continuous, then $\Phi$ has a fixed point.
	\end{theorem}

	Therefore, the existence of an NE follows from the above Theorem.

@@

	Let us return to the definition of $\alpha_i$, which I repeat here for convenience

	\begin{equation*}
		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} x_i(t') \, dt'
	\end{equation*}

@@

	Now, we since we can rewrite the best response function $BR_i$ as $\arg\max_{y \in \Delta_i} \bar{u}_i(y, (w_{-i}^T \otimes I_n) \begin{bmatrix}
		x_1 \\ . \\ . \\ . \\ x_N
	\end{bmatrix})$, we can rewrite the CTFP condition as, for all $i$ and all $t \geq 1$

	\begin{equation}
		m_i(t) \in BR_i((w_{-i}^T \otimes I_n) \begin{bmatrix}
			x_1 \\ . \\ . \\ . \\ x_N
		\end{bmatrix})
	\end{equation}

	This gives

	\begin{equation}
		\Dot{\alpha}_i(t) \in \frac{1}{t} (BR_i((w_{-i}^T \otimes I_n) \begin{bmatrix}
			x_1 \\ . \\ . \\ . \\ x_N
		\end{bmatrix}) - \alpha_i(t))
	\end{equation}

>>>>

	To show existence of an NE we will need the following definition and Theorem.

	\begin{definition}[Upper Semi-Continuous]
		A compact-valued correspondence $\Phi: A \rightarrow B$ is \emph{upper semi-continuous} at a point $a$ if $g(a)$ is non-empty and if, for every sequence $a_n \rightarrow a$ and every sequence $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a convergent subsequence of $(b_n)$ whose limit point $b$ is in $g(a)$.  
	\end{definition}

	\begin{theorem}[Kakutani]
		Let $K \subset \mathbb{R}^n$ be compact and convex and $\Phi: K \rightarrow K$ be closed or upper semi-continuous, with nonempty, convex and compact values. Then $\Phi$ has a fixed point.
	\end{theorem}

	Note that, when active on a simplex, the function $\Phi: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes the nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.

	\begin{theorem}[Existence of NE]
		Under the assumption (II), namely that the payoff function achieves a bilinear property, a Nash Equilibrium $\{x_i^*\}_{i = 1}^N$ exists.
	\end{theorem}

	\begin{proof}
		We begin by rewriting the NE condition by concatenating the set of NE vectors into one long colunn vector. This gives

@@

		in which $w_{-i}$ is a column vector containing $w_{ij}$ in the $j$'th element for all $j \in N(i)$ and 0 everywhere else (including in the $i$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product. For example, the form for agent 1, in the case of 2-action game is given by

		\begin{equation}
			(w_{-1}^T \otimes I_2) = [0, w_{12}, w_{13}, ..., w_{1n}] \otimes I_2 = 
			\begin{bmatrix}
				0 & 0 & w_{12} & 0 & ... & w_{1n} & 0 \\
				0 & 0 & 0 & w_{12} & ... & 0 & w_{1n} \\
			\end{bmatrix}
		\end{equation}

		So our condition becomes
		\begin{equation}
			\begin{bmatrix}
				x_1^* \\ . \\ . \\ . \\ x_N^*
			\end{bmatrix} \in
			\begin{bmatrix}
				\arg\max_{y \in \Delta_1} \bar{u}_1(y, (w_{-1}^T \otimes I_n) \begin{bmatrix}
					x_1^* \\ . \\ . \\ . \\ x_N^*
				\end{bmatrix}) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n) \begin{bmatrix}
				x_1^* \\ . \\ . \\ . \\ x_N^*
			\end{bmatrix}))
			\end{bmatrix}	.
		\end{equation}

@@

		Now, since the modified payoff $\bar{u}$ shares the same bilinear property as $u$, we can assert that it is continuous is its second argument. Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous. This continuity can be extended to the above concatenation of best responses. As such, we can apply Kakutani's Fixed Point Theorem to assert that the above map admits a fixed point.

	\end{proof}

@@

	\begin{theorem}
		There exists a path $m$ which satisfies the property that, for all $i$, $m_i \in BR_i
		(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
	\end{theorem}

	\begin{proof}
		Recall the definition of $\alpha_i(t)$

		\begin{equation*}
		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} m_i(t') \, dt'
		\end{equation*}

@@

		Now we assert that $m_i(t) \in BR_i(\alpha_{\sigma_t}) = \arg\max_{y \in \Delta_i} u_i(y,
		w_{ii} \alpha_i(t) + \sum_{j \in N(i)} w_{ij} \alpha_j(t))$.

		Let us then define $\alpha(t)$ as the concatenation of all $\alpha_i(t)$

		\begin{equation}
			\alpha(t) = \begin{bmatrix}
				\alpha_1(t)^T, \ldots, \alpha_N(t)^T
			\end{bmatrix}^T \subset \mathbb{R}^{Nn}
		\end{equation}

		We can, therefore, write the aggregation as

		\begin{equation}
			(W \otimes I_n) \alpha(t) = \begin{bmatrix}
				\sum_{j \in N(1)} w_{1j} \alpha_j(t) \\
				.\\
				.\\
				.\\
				\sum_{j \in N(N)} w_{Nj} \alpha_j(t)
			\end{bmatrix} \subset \mathbb{R}^{Nn}
		\end{equation}

		I will write $(W \otimes I_n) \alpha(t)$ as $\alpha_W$ for convenience. Furthermore, using
		the bimatrix property of the game, we can say that

		\begin{equation}
			\begin{bmatrix}
				\arg\max_{y \in \Delta_1} y \cdot A_1 ( \alpha_W(t)_1) \\
				.\\
				.\\
				.\\
				\arg \max_{y \in \Delta_N} y \cdot A_n (\alpha_W(t)_N) 
			\end{bmatrix} = 
			\arg \max_{y \in \Delta} y \cdot \begin{bmatrix}
				A_1 & 0 & . & . & . & 0 \\
				0 & A_2 & . & . & . & 0 \\
				& & . & & & \\
				& & & . & & \\
				& & & & . & \\
				0 & 0 & . & . & . & A_N \\
			\end{bmatrix} \alpha_W(t) = \arg\max_{y \in \Delta} y \cdot \Lambda (W \otimes I_n)
			\alpha(t)
		\end{equation}

		in which $\Delta = \times_i \Delta_i$ and $\Lambda$ is the block diagonal matrix containing
		each $A_i$.

		We can now write the differential inclusion as

		\begin{equation}
			\dot{\alpha(t)} \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
			I_n)
			\alpha(t) \}- \alpha(t))
		\end{equation}

		with the initial condition $\alpha(1) = \mu$. Then, the path $m$ is a CTFP if its
		corresponding $\alpha(t; m)$ is a solution to the above differential inclusion. Following
		the definition of (Harris 1998), a solution $\alpha(t)$ must satisfy

		\begin{enumerate}
			\item $\alpha(t)$ is locally Lipschitz
			\item $\alpha(1) = \mu$
			\item $\dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
			I_n)
			\alpha(t) \}- \alpha(t))$ for almost all $t \in [1, \infty)$ 
		\end{enumerate}

		The question then remains, does the differential inclusion admit a solution? Using the
		results of Aubin and Cellina (see Harris 1998, paragraph below Prop. 6), can use the fact
		that the $\arg \max$ function is non-empty, compact and convex valued, bounded (all of
		these follow since the function acts from $\Delta$ to $\Delta$) and upper semi-continuous.
		With these facts in place, we can say that there is a CTFP for any initial value $\mu$.
		\ah{I believe this holds for any choice of $W$ as long as it is row stochastic so that
		the values remain inside $\Delta$ after aggregation}.
	\end{proof}

	\section*{Convergence Properties}

	I've spent some time trying to show convergence of the CTFP to a Nash Equilibrium, without the
	requirement that $w_{ii} = 0$. Unfortunately, it doesn't look like that is the case in general,
	at least with the other assumptions that we have made. Perhaps changing the requirement of the
	payoff functions or the aggregation method (e.g. to a non-linear one) would influence this, but
	for the bimatrix games that we've looked at so far, no luck.
	We can, however, say that there is a fixed point since the solution $\alpha(t; m)$, for any CTFP
	$m$ maps from a compact space to itself. Therefore, any sequence $\{\alpha(\tau_q; m)\}$ where
	$\tau_q \rightarrow \infty$ as $q \rightarrow \infty$ has all of its elements inside a compact
	set. Therefore, by the Bolzano-Wierstrass Theorem, this sequence has at least one limit point.
	We can say that this limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
	determine any other structure of the limit point for when this does not hold. For example, is it
	part of the `no regret' set?
